---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# yarraWQ

yarraWQ is an R package designed to make the Yarra River Water Quality dataset easy to use and explore. It provides clean, ready-to-analyze data, helper functions for visualization, and an interactive Shiny app for exploring trends in water parameters over time and across sites.

## Installation

You can install the development version of yarraWQ from [GitHub](https://github.com/) with:

```{r}
# install.packages("pak")
pak::pak("ETC5523-2025/assignment-4-packages-and-shiny-apps-RuoWei-ctrl")
```

## Example

Here’s how to explore the included dataset:

```{r example, message=FALSE, warning=FALSE, eval=FALSE}
library(yarraWQ)
head(yarra_wq)

# filter just pH measurements
filtered <- filter_yarra_data(yarra_wq, parameter_name = "pH")
head(filtered)
```

Generate a simple time-series plot for a selected water quality parameter (for example, pH):

```{r plot-example, message=FALSE, warning=FALSE, eval=FALSE}
plot_yarra_metric(parameter_name = "pH")
```

This function allows you to quickly visualize long-term water quality changes in the Yarra River.

## Shiny App

For interactive exploration, you can launch the Shiny app:

```{r shiny-app, message=FALSE, warning=FALSE, eval=FALSE}

run_yarra_app()
```

The app allows users to:

-   Select a parameter and site

-   View corresponding time trends

-   Compare results across multiple monitoring stations

## Data Source

The dataset (`yarra_wq`) was adapted from your course-provided data file **yarra_wq_clean.csv**, representing long-term monitoring records of the Yarra River’s water quality.\
Variables include pH, temperature, turbidity, dissolved oxygen, and more.
